A Transformer Model for Retrosynthesis

### 2019-05-09 papers/retrosynthesis/article.tex
misprints
for ICAN conf uncomment commands to make header and footer empty.
check links to final models

\title{A Transformer Model for Retrosynthesis}
\date{April 5, 2019}

@@

@@

\begin{abstract}
We describe a Transformer model for a retrosynthetic reaction prediction task. 
The model is trained on 45\,033 experimental reaction examples extracted 
from USA patents. It can successfully predicts the reactants set for 
42.7\% of cases on the external test set. During the training procedure, we applied 
different learning rate schedules and snapshot learning. These techniques can prevent 
overfitting and thus can be a reason to get rid of internal validation dataset that 
is advantageous for deep models with millions of parameters. We thoroughly investigated different 
approaches to train Transformer models and found that snapshot learning with averaging weights on 
learning rates minima works best.  While decoding the model output probabilities there is a strong 
 influence of the temperature that improves at T=1.3 the accuracy of models up to 1-2\%. 
\end{abstract}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 16.5cm]{images/t1-1.pdf}
  \caption{Learning curves and rate schedule for T1 model. Losses for training and validation datasets on the left, usual learning rate schedule on the right.}
  \label{fig:t11}
\end{figure}

\begin{table}[h!]
\caption{Parameters of T11 run.}
  \centering
  \begin{tabular}{p{6.2cm}p{3.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss (training / validation) &  0.09345 / 0.10864 & & & \\
    Last training loss (training / validation) &  0.05867 / 0.11819& & & \\
    Epoch (early stopping) & 208 & & & \\
    \midrule
    Greedy search (early stopping, epoch 208) & & 32.83 & &\\
    Greedy search (last, epoch 999) & & 34.75 & & \\
    Greedy (last 10 average, epoch, 990 - 999) & & 35.57 & & \\
    \midrule
    Beam, T = 1.0 (early) & & 35.57 & 54.14 & 59.13 \\
    Beam, T = 1.3 (early) & & 35.93 & 54.59 & 59.51 \\ 
    \midrule
    Beam, T = 1.0 (last) & & 37.15 & 55.22 &  60.49 \\
    Beam, T = 1.3 (last) & & 37.67 & 55.97 & 61.01 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & & 37.83 & 56.08 &  60.63 \\
    \textbf{Beam, T = 1.3 (last 10 average)}  & & \textbf{38.15} & \textbf{56.71} & \textbf{61.31} \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-1-early.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-1-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-1-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-2-early.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-2-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-2-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-3-early.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-3-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t1-3-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-1-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-1-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-2-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-2-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-3-last.h5}

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t2-3-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t3-1.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t3-2.h5}
\newpage

@@

\url{https://github.com/bigchem/retrosynthesis/papers/retrosynthesis/models/t3-3.h5}

>>>>

\title{A Transformer Model for Retrosynthesis}

@@

%\rhead{}
%\chead{}
%\cfoot{}
%\renewcommand{\headrulewidth}{0.0pt}

@@

\begin{abstract}
We describe a Transformer model for a retrosynthetic reaction prediction task. 
The model is trained on 45\,033 experimental reaction examples extracted 
from USA patents. It can successfully predict the reactants set for 
42.7\% of cases on the external test set. During the training procedure, we applied 
different learning rate schedules and snapshot learning. These techniques can prevent 
overfitting and thus can be a reason to get rid of internal validation dataset that 
is advantageous for deep models with millions of parameters. We thoroughly investigated different 
approaches to train Transformer models and found that snapshot learning with averaging weights on 
learning rates minima works best.  While decoding the model output probabilities there is a strong 
 influence of the temperature that improves at T=1.3 the accuracy of models up to 1-2\%. 
\end{abstract}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width = 16.5cm]{images/t1-1.pdf}
  \caption{Learning curves and rate schedule for T1 model. Losses for training and validation datasets on the left, usual learning rate schedule on the right.}
  \label{fig:t11}
\end{figure}
\vspace{-0.5cm}
\begin{table}[h!]
\caption{Parameters of T11 run.}
  \centering
  \begin{tabular}{p{6.2cm}p{3.5cm}p{1.5cm}p{1.5cm}p{1.5cm}}
    \toprule
    Parameter & Value & Top-1 & Top-3 & Top-5 \\
    \midrule
    Early stopping loss (training / validation) &  0.09345 / 0.10864 & & & \\
    Last training loss (training / validation) &  0.05867 / 0.11819& & & \\
    Epoch (early stopping) & 208 & & & \\
    \midrule
    Greedy search (early stopping, epoch 208) & & 32.83 & &\\
    Greedy search (last, epoch 999) & & 34.75 & & \\
    Greedy (last 10 average, epoch, 990 - 999) & & 35.57 & & \\
    \midrule
    Beam, T = 1.0 (early) & & 35.57 & 54.14 & 59.13 \\
    Beam, T = 1.3 (early) & & 35.93 & 54.59 & 59.51 \\ 
    \midrule
    Beam, T = 1.0 (last) & & 37.15 & 55.22 &  60.49 \\
    Beam, T = 1.3 (last) & & 37.67 & 55.97 & 61.01 \\ 
    \midrule
    Beam, T = 1.0 (last 10 average) & & 37.83 & 56.08 &  60.63 \\
    \textbf{Beam, T = 1.3 (last 10 average)}  & & \textbf{38.15} & \textbf{56.71} & \textbf{61.31} \\ 
    \bottomrule
  \end{tabular}
  \label{tbl:t11}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-1-early.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-1-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-1-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-2-early.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-2-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-2-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-3-early.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-3-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t1-3-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-1-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-1-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-2-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-2-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-3-last.h5}

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t2-3-avg.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t3-1.h5}

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t3-2.h5}
\newpage

@@

\url{https://github.com/bigchem/retrosynthesis/tree/master/papers/retrosynthesis/models/t3-3.h5}
